Verifying Demonstrations

### 2018-05-31 paper/conclusions.tex
anon-pass explanation, future work tamarin

>>>>

For future work, a recently published model for formal verification
of distance-bounding protocols~\cite{TamarinDB} looks promising to
analyze and strengthen the properties of our protocol, especially once
the model and tool are extended to include terrorist-fraud attacks and
other formalizations of attacks and protocol properties as outlined as
future work by the authors.
